Higher-Order unification for free!

### 2024-04-10 paper/main.tex
w
remove trivial decomp

\subsection{Memory (\mapStore) and substitution ($\rho$ and $\sigma$)}
\label{sec:grounwork}

@@

\noteE{What is commit-links and complete-mapping?}

\noindent
Decompiling an assignment requires to turn abstractions into
lambdas. For aesthetic purposes we also eta-contract the result
(not needed since \Fo{} equality can do that)

\input{code/decompm}

\noindent
Finally decompiling a term is trivial, now that we have an extended
mapping containing all unassigned variables \Ue may have introduced.

\input{code/decomp}

\noindent
Note that we use beta to build fapp nodes when needed (if Ag is empty
no \elpiIn{fapp} node should appear).

>>>>

\subsection{Memory map (\mapStore) and substitution ($\rho$ and $\sigma$)}
\label{sec:grounwork}

@@

\todo{commit links + complete-map + abs to lam}
% \noteE{What is commit-links and complete-mapping?}

% \noindent
% Decompiling an assignment requires to turn abstractions into
% lambdas. For aesthetic purposes we also eta-contract the result
% (not needed since \Fo{} equality can do that)

% \input{code/decompm}

% \noindent
% Finally decompiling a term is trivial, now that we have an extended
% mapping containing all unassigned variables \Ue may have introduced.

% \input{code/decomp}

% \noindent
% Note that we use beta to build fapp nodes when needed (if Ag is empty
% no \elpiIn{fapp} node should appear).
